### 2019-07-18 manuscript/methods.tex
All co-authors input added, figures corrected

Chromosome number data were obtained for all Solanaceae taxa in the Chromosome Counts Database \citep[CCDB;][]{rice_2015}, and the ca.~14,000 records were curated semi-automatically using the \mbox{CCDBcurator} R package \citep{rivero_2019}.
CCDB contains records from original sources that have multiple complex symbol patterns denoting multivalence, or irregularites of chromosome counts.
After a first round of automatic cleaning, we examined results by hand and corrected records as necessary.
Our hand-curated records were also contrasted against the ploidy dataset from \citet{robertson_2011}, original references therein, and against ploidy data in the C-value DNA dataset from \citet{bennett_2005}.
By comparing three different sources of information, we were able to code taxa as diploid, $D$, or polyploid, $P$.
For the majority of species, ploidy was assigned according to information from the original publications included in the  C-value DNA dataset \citep{bennett_2005}.
For taxa without ploidy information but with information about chromosome number, we assigned ploidy based on the multiplicity of chromosomes within the genus/family, or based on SI/SC classification.
For example, \textit{Solanum betaceum} did not have information about ploidy level but it has 24 chromosomes, so since $x=12$ is the base chromosome number of the genus \textit{Solanum} \citep{olmstead_2007}, we assigned \textit{S.~betaceum} as diploid. 
Additionally, because of the absence of SI polyploids (explained above and below), species known to be SI could be scored as diploid.
Species with more than one ploidy level were assigned the most frequent ploidy level recorded or the smallest ploidy in case of frequency ties.

Breeding system states were scored as self-incompatible, $I$, or self-compatible, $C$, based on results curated from the literature and original experimental crosses \citep[as compiled in][]{igic_2006, goldberg_2010, robertson_2011, goldberg_2012}.
Most species could unambiguously be coded as either $I$ or $C$ \citep{raduski_2012}.
Following previous work, we coded any species with a functional SI system as $I$, even if SC or dioecy was also reported.
Dioecious species without functional SI were coded as $C$.
% E: I am trying to stick with I/C when talking about the state values, but using SI/SC when talking about the meaning of the trait (because this what people use normally). 
%R- Okay- I was getting confused as well thanks for clarifying

@@

We additionally fit three models in which both ploidy and a hidden trait could influence diversification (M3--M5).
These models differ in whether transitions between the hidden states are symmetric or asymmetric, and whether the polyploidization rate depends on the hidden state.
Comparing M1--M5 allows us to test whether ploidy is associated with diversification differences on top of the differences potentially explained by an unknown factor (\cref{table:bayesfactors}).

We further fit the analogues of these five models but including a rate parameter $\delta$ for transitions from polyploid to diploid (M6--M10,  \cref{supptable:M6M10}).
These comparisons allow us to assess whether our conclusions about ploidy and diversification are robust to the possibility of diploidization.

@@

We then add models to allow diversification to be influenced by only a hidden trait (M12), or by both breeding system and a hidden trait (M13--M15, with varying degrees of complexity in the hidden trait transitions \cref{table:M11M15}).
Similar models were used by \citet{freyman_2017} used to study diversification in Onagraceae.

Self-incompatibility is homologous in all Solanaceae species in which S-alleles have been cloned and controlled crosses performed.
All species sampled to date possess a non-self recognition, RNase-based gametophytic self-incompatibility \citep[shared even with other euasterid families;][]{ramanauskas_2017}.
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism at the locus that controls the SI response \citep{ioerger_1990, igic_2006}.
Thus, there is strong evidence in Solanaceae that the $I$ state is ancestral in the family, and that the SI mechanism was not regained.
Therefore, for all breeding system models, we estimated a transition rate from $I$ to $C$  but not the reverse ($q_{CI}=0$).
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
%
%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head. 
%B: Whew, I was worried. Er, "friend" says thanks. R- Your welcome, by mistake I did that model with reversibility from C to I. I didn't run it for as long as the rest but preliminary ancestral reconstructions seem almost identical when you add that parameter than when you don't.

@@

As for the previous models of only one trait, we then allow diversification to be influenced by only a hidden trait (M17), or by ploidy, breeding system, and a hidden trait (M18--M20) with varying degrees of complexity in the hidden trait transitions (\cref{supptable:M16M20}).
We add this hidden trait layer on top of our three-state model \citep[similar to][]{caetano_2018, huang_2018}.
We also fit the analogous models but allowing for diploidization (M21--M25, \cref{supptable:M21M25}).

@@

The models described so far allow us to assess the contributions of our two focal characters---ploidy and breeding system---to lineage diversification, but they do not reveal whether it is valuable to include both characters in the analysis.
To answer this question with statistical model comparisons requires comparing the likelihood of the data given each model.
This is impossible for the ploidy and breeding system models presented so far, however, because the data are different for the different models: they use either the $D/P$ or the $I/C$ or the $IC/CD/CP$ state spaces.
Therefore, the use of different data results in incomparable models.

In order to compare fits of ploidy-only \vs breeding system-only \vs combined trait models, we use the technique of `lumping' states together \citep{tarasov_2019}.
We use the state space of the $IC/CD/CP$ model but constrain the rate parameters to mimic the behavior of the single-trait models.
First we lump together $ID$ and $CD$ to form the diploid state, mimicking the $D/P$ model (M26).
Then we lump together $CD$ and $CP$ to form the self-compatible state, mimicking the $I/C$ model (M28).
We further add a hidden character to each of these models (M27 and M29), and then compare this group of models (\cref{table:lumped}).

We do not include additional models with diploidization because this reverse ploidy transition renders the models non-lumpable.
To lump states requires that the transition rates from the lumped state to the singular state be equal \citep{tarasov_2019}.
When including diploidization, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
Because $ID$ and $CD$ would be lumped to mimic the $D/P$ model, this model is non-lumpable when $\delta \ne 0$.
When lumping $CD$ and $CP$, however, the transition rate to $ID$ is zero for both, so the SC states are lumpable. 
Thus, we can compare models to test whether it is advantageous to include both traits, but only when ignoring diploidization.
% E: Below was all good, but it seemed like more detail than necessary.
% Then we define a single parameter $q_0$ going into the lumped state $(CD,CP)$ as the new rate from SI to SC.
% This defines the lumped model M28 (\cref{figure:lumped}E) that is equivalent to M1 but comparable to M16.
% We repeat this process to create the lumped model M26 for $D/P$ by restricting the polyploidy rate to be $rho_0$ out of the lumped state $(ID,CD)$.
% When including diploidization, however, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
% Since $\delta \neq 0$, the models with diplodization cannot be lumped to be compared to the three-state models.

@@

Considering ploidy and breeding system together, there are two evolutionary pathways from SI diploid to SC polyploid \citep{brunet2001, robertson_2011}.
In the one-step pathway, the $CP$ state is produced directly from the $ID$ state when whole genome duplication disables SI.
In the two-step pathway, the $CD$ state is an intermediate: SI is first lost, and later the SC diploid undergoes polyploidization.
We quantify the relative contribution of these pathways to polyploidy in two ways, each using the median estimates of rates from the simplest model that includes both traits (M16).

@@

First, we consider only the rates of transitions between these states, placing them in the propagation matrix \myvec{Q}.
The matrix $\myvec{P} = \exp(\myvec{Q} t)$ then provides the probabilities of changing from one state to any other state after time $t$.
Closed-form solutions for the two pathway probabilities are provided in \citet{robertson_2011}.
Our results will differ from those of \citet{robertson_2011} because our transition rate estimates come from a dated phylogeny and a model that allows for state-dependent diversification.

Second, we consider not only transitions between states but also diversification within each state.
State-dependent diversification can change the relative contributions of the two pathways.
For example, if the net diversification rate is small for $CD$, the two-step pathway will contribute relatively less.
We therefore include the difference between speciation and extinction along the diagonal elements of the propagation matrix.
As before, matrix exponentiation provides the relative chance of changing from one state to any other state after time $t$.
The calculations of the propagation matrix are not probabilities because diversification changes the number of lineages as time passes. 
%B: FIXME, we'll hear complaints again about "this," "these," and ... "their." (below)
% R- fixed
We can still use ratios, however, to consider the relative contribution of each pathway, analogous to the normalized age structure in a growing population. % R- here a reference would be nice  E: Does Jake have a favorite ref? Otherwise, I guess a basic ecology textbook.
%
% E & R todo ?: for the case with net div, write out the propagation matrix and equations for pathway contributions
% R- couldn't solve to get the exact solutions turns out it is really hard.
%
% E: I don't think we need this section now that diploidization is in each of the sections above.  But I'm saving this text in case we want to put some of it in Results.
%--------------------------------------------------
% \subsubsection{Diploidization as an exploratory hypothesis}
%
% The models described above allow polyploidization but not its reverse.
% We explored the effects of allowing diploidization by adding a parameter $\delta$ for transitions from $P$ back to $D$ (in the $D/P$ and $D/P+A/B$ models) or from $CP$ back to $CD$ (in the $I/C$ and $I/C+A/B$ models); we did not allow transitions from $CP$ back to $ID$ because that would include regain of SI.
% Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}, which assume only aneuploid change and polyploidization.
% Our ploidy classifications, however, when possible also incorporated information on chromosome multiplicity at the genus level and author conclusions within original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution).
% Since it is not known whether diploidization can be detected under these additional ploidy classifications, we fit models with and without diploidization in order to test whether the conclusions about diversification are sensitive to including diploidization.
% In our models, the diploidization parameter (or its absence, $\delta=0$), represents an opportunity to explore a possibly significant assumption that may not decisively affect interactions among ploidy, breeding system, and diversification.
%--------------------------------------------------

@@

Parameters for each of the 29 models were coded as graphical models and Bayesian statistical inference was performed RevBayes \citep{hoehna_2016}.
Scripts for analyses and key results are available as Supplementary Information. % FIXME more permanent than \url{https://github.com/roszenil/solploidy}.- Happens after publication
We accounted for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $651/3000$ \citep[using the method of][]{fitzjohn_2009} since the Solanaceae family has approximately 3,000 species \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the models.
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters in \cref{figure:netdivall}, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses every 100 generations.
Ancestral state estimations for all models show the maximum \emph{a posteriori} estimates of the marginal probability distributions for each of the 650 internal nodes for each of the models in \cref{figure:netdivall}. (\cref{suppfigure:DPnodipasr,suppfigure:DPnodipABasr,suppfigure:ICasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPnodipABasr}).

>>>>

Chromosome number data were obtained for all Solanaceae taxa in the Chromosome Counts Database \citep[CCDB;][]{rice_2015}, and the ca.~14,000 records were curated semi-automatically using the \mbox{CCDBcurator} R package \citep{rivero_2019}.
CCDB contains records from original sources that have multiple complex symbol patterns denoting multivalence, or irregularites of chromosome counts.
After a first round of automatic cleaning, we examined results by hand and corrected records as necessary.
Our hand-curated records were also contrasted against the ploidy dataset from \citet{robertson_2011}, original references therein, and against ploidy data in the C-value DNA dataset from \citet{bennett_2005}.
By comparing three different sources of information, we were able to code taxa as diploid, $D$, or polyploid, $P$.
For the majority of species, ploidy was assigned according to information from the original publications included in the  C-value DNA dataset \citep{bennett_2005}.
For taxa without ploidy information but with information about chromosome number, we assigned ploidy based on the multiplicity of chromosomes within the genus/family, or based on SI/SC classification.
For example, \textit{Solanum betaceum} did not have information about ploidy level but it has 2n=24 chromosomes, so since $x=12$ is the base chromosome number of the genus \textit{Solanum} \citep{olmstead_2007}, we assigned \textit{S.~betaceum} as diploid. 
Additionally, because of the absence of SI polyploids (explained above and below), species known to be SI could be scored as diploid.
Species with more than one ploidy level were assigned the most frequent ploidy level recorded or the smallest ploidy in case of frequency ties.

Breeding system states were scored as self-incompatible, $I$, or self-compatible, $C$, based on results curated from the literature \citep[as compiled in][]{igic_2006, goldberg_2010, robertson_2011, goldberg_2012}. %IM suggestion
Most species could unambiguously be coded as either $I$ or $C$ \citep{raduski_2012}.
Following previous work, we coded any species with a functional SI system as $I$, even if SC or dioecy was also reported.
Dioecious species without functional SI were coded as $C$.
% E: I am trying to stick with I/C when talking about the state values, but using SI/SC when talking about the meaning of the trait (because this what people use normally). 
%R- Okay- I was getting confused as well thanks for clarifying

@@

We additionally fit three models in which both ploidy and a hidden trait could influence diversification (M3--M5).
These models differ in whether transitions between the hidden states are symmetric (M3) or asymmetric(M4), and whether the polyploidization rate depends on the hidden state(M5). %WF suggestion
Comparing M1--M5 allows us to test whether ploidy is associated with diversification differences on top of the differences potentially explained by an unknown factor.

We further fit the analogues of these five models but including a rate parameter $\delta$ for transitions from polyploid to diploid (M6--M10).
These comparisons allow us to assess whether our conclusions about ploidy and diversification are robust to the possibility of diploidization.

@@

We then add models to allow diversification to be influenced by only a hidden trait (M12), or by both breeding system and a hidden trait (M13--M15, with varying degrees of complexity in the hidden trait transitions \cref{table:M11M15}).
Similar models were used by \citet{freyman_2019} to study diversification in Onagraceae.

Self-incompatibility is homologous in all Solanaceae species in which S-alleles have been cloned and controlled crosses performed.
All species sampled to date possess a non-self recognition, RNase-based gametophytic self-incompatibility \citep[shared even with other euasterid families;][]{ramanauskas_2017}.
Furthermore, species that are distantly related within this family carry closely-related alleles, with deep trans-specific polymorphism at the locus that controls the SI response \citep{ioerger_1990, igic_2006}.
Thus, there is strong evidence in Solanaceae that the $I$ state is ancestral in the family, and that the SI mechanism was not regained.
For all breeding system models, we estimated a transition rate from $I$ to $C$  but not the reverse ($q_{CI}=0$).
% This is an important assumption because ancestral state reconstruction in the models might differ when polyploidy and breeding system are analyzed as independent in the Solanaceae tree.
%
%B: What happens if SC->SI is not fixed? Asking for a friend.  E: Surprisingly, Rosana reports, results are not turned on their head. 
%B: Whew, I was worried. Er, "friend" says thanks. R- Your welcome, by mistake I did that model with reversibility from C to I. I didn't run it for as long as the rest but preliminary ancestral reconstructions seem almost identical when you add that parameter than when you don't.

@@

As for the previous models of only one trait, we then allow diversification to be influenced by only a hidden trait (M17), or by ploidy, breeding system, and a hidden trait (M18--M20) with varying degrees of complexity in the hidden trait transitions
\citep[similar to][]{caetano_2018, huang_2018}. %IM suggestion
We also fit the analogous models but allowing for diploidization (M21--M25).

@@

The models described so far allow us to assess the contributions of our two focal characters---ploidy and breeding system---to lineage diversification, but they do not reveal whether it is valuable to include both characters in the analysis.
To answer this question with statistical model comparisons requires comparing the likelihood of the data given each model.
This is impossible for the ploidy and breeding system models presented so far, however, because the data are different for the different models: they use either the $D/P$ or the $I/C$ or the $ID/CD/CP$ state spaces.
Therefore, the use of different data results in incomparable models.

In order to compare fits of ploidy-only \vs breeding system-only \vs combined trait models, we use the technique of `lumping' states together \citep{tarasov_2019}.
We use the state space of the $ID/CD/CP$ model but constrain the rate parameters to mimic the behavior of the single-trait models.
To lump states requires that the transition rates from the lumped state to the singular state be equal \citep{tarasov_2019}.
First we lump together $ID$ and $CD$ to form the diploid state, mimicking the $D/P$ model (M26). 
Proposing a lumped ploidy model by aggregating $ID$ and $CD$ requires forcing the rate of polyploidization from $ID$ and $CD$ to $CP$ to be equal (i.e. $\rho_0=\rho_I=\rho_c$), but also requires
assuming that the rates of speciation and extinciton for $ID$ and $CD$ to be equal.
Therefore, we define the new parameters $\lambda_D$ and $\mu_D$  that are the same for each of the two diploid states $ID$ and $CD$.%IM suggestion, describe more the lumping
We used the same procedure to lump together $CD$ and $CP$ to form the self-compatible state, mimicking the $I/C$ model (M28).
In this particular case, the rate from $CD$ to $CP$ back to $ID$ is zero and equal for both, so the model is lumpable. 
However, to fully mimic the breeding system model, we assume that the rate of selfing is equal (i.e. $q_0=q_{IC}=rho_I$) and the rates
of speciation and extinction for both $CD$ and $CP$ are the same (new parameters $\lambda_C$ and $\mu_C$).
We further add a hidden character to each of these models (M27 and M29), and then compare this group of models (\cref{table:lumped}).

We do not include additional models with diploidization because this reverse ploidy transition renders the models non-lumpable.
When including diploidization, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
Because $ID$ and $CD$ would be lumped to mimic the $D/P$ model, this model is non-lumpable when $\delta \ne 0$.
Thus, we can compare models to test whether it is advantageous to include both traits, but only when ignoring diploidization.
% E: Below was all good, but it seemed like more detail than necessary.
% Then we define a single parameter $q_0$ going into the lumped state $(CD,CP)$ as the new rate from SI to SC.
% This defines the lumped model M28 (\cref{figure:lumped}E) that is equivalent to M1 but comparable to M16.
% We repeat this process to create the lumped model M26 for $D/P$ by restricting the polyploidy rate to be $rho_0$ out of the lumped state $(ID,CD)$.
% When including diploidization, however, transitions from $CP$ to $CD$ are at rate $\delta$ but transitions from $CP$ to $ID$ do not occur.
% Since $\delta \neq 0$, the models with diplodization cannot be lumped to be compared to the three-state models.

@@

Considering ploidy and breeding system together, there are two evolutionary pathways from SI diploid to SC polyploid \citep{brunet2001, robertson_2011}.
In the one-step pathway, the $CP$ state is produced directly from the $ID$ state when whole genome duplication disables SI.
In the two-step pathway, the $CD$ state is an intermediate: SI is first lost, and later the SC diploid undergoes polyploidization.
We quantify the relative contribution of these pathways to polyploidy in two ways, each using the median estimates of rates from the simplest model that includes both traits (M16). Our results will differ from those of \citet{robertson_2011} because our transition rate estimates come from a dated phylogeny and a model that allows for state-dependent diversification. %IM suggestion

@@

First, we consider only the rates of transitions between these states, placing them in the propagation matrix \myvec{Q}.
The matrix $\myvec{P} = \exp(\myvec{Q} t)$ then provides the probabilities of changing from one state to any other state after time $t$.
Closed-form solutions for the two pathway probabilities are provided in \citet{robertson_2011}.

Second, we consider not only transitions between states but also diversification within each state.
State-dependent diversification can change the relative contributions of the two pathways.
For example, if the net diversification rate is small for $CD$, the two-step pathway will contribute relatively less.
We therefore include the difference between speciation and extinction along the diagonal elements of the propagation matrix.
As before, matrix exponentiation provides the relative chance of changing from one state to any other state after time $t$.
The calculations of the propagation matrix are not probabilities because diversification changes the number of lineages as time passes. 
%B: FIXME, we'll hear complaints again about "this," "these," and ... "their." (below)
% R- fixed
We can still use ratios, however, to consider the relative contribution of each pathway, analogous to the normalized age structure in a growing population \citep{leslie_1945}.
 % R- here a reference would be nice  E: Does Jake have a favorite ref? Otherwise, I guess a basic ecology textbook.-DONE
%
% E & R todo ?: for the case with net div, write out the propagation matrix and equations for pathway contributions
% R- couldn't solve to get the exact solutions turns out it is really hard.
%
% E: I don't think we need this section now that diploidization is in each of the sections above.  But I'm saving this text in case we want to put some of it in Results.
%--------------------------------------------------
% \subsubsection{Diploidization as an exploratory hypothesis}
%
% The models described above allow polyploidization but not its reverse.
% We explored the effects of allowing diploidization by adding a parameter $\delta$ for transitions from $P$ back to $D$ (in the $D/P$ and $D/P+A/B$ models) or from $CP$ back to $CD$ (in the $I/C$ and $I/C+A/B$ models); we did not allow transitions from $CP$ back to $ID$ because that would include regain of SI.
% Previous modeling approaches \citep{mayrose_2011} have argued against inferring diploidization rates when using ploidy data that comes from classifications based on chromosome number multiplicity or chromosome number change models like chromEvol \citep{mayrose_2010, glick2014, mayrose_2015, freyman_2017}, which assume only aneuploid change and polyploidization.
% Our ploidy classifications, however, when possible also incorporated information on chromosome multiplicity at the genus level and author conclusions within original studies with alternative sources of information (\eg geographic distribution, genus ploidy distribution).
% Since it is not known whether diploidization can be detected under these additional ploidy classifications, we fit models with and without diploidization in order to test whether the conclusions about diversification are sensitive to including diploidization.
% In our models, the diploidization parameter (or its absence, $\delta=0$), represents an opportunity to explore a possibly significant assumption that may not decisively affect interactions among ploidy, breeding system, and diversification.
%--------------------------------------------------

@@

Parameters for each of the 29 models were coded as graphical models and Bayesian statistical inference was performed with RevBayes \citep{hoehna_2016}.
Scripts for analyses and key results are available as Supplementary Information. % FIXME more permanent than \url{https://github.com/roszenil/solploidy}.- Happens after publication
We accounted for incomplete sampling in all analyses by setting the probability of sampling a species at the present to $651/3000$ \citep[using the method of][]{fitzjohn_2009} since the Solanaceae family has approximately 3,000 species \citep{solsource}.
For all models, we assumed that speciation and extinction parameters had log-normal prior distributions with means equal to the expected net diversification rate $(\text{number of taxa} / [2 \times \text{root age}])$ and standard deviation $0.5$.
Priors for parameters defining trait changes were assumed to be gamma distributed with parameters $k=0.5$ and $\theta=1$. 
For each model, a Markov chain Monte Carlo \citep[MCMC;][]{metropolis1953equation,Hastings1970} was run in the high-performance computational cluster at the Minnesota Supercomputing Institute, which allowed for 5,000 generations of burn-in and a minimum of 200,000 generations of MCMC for each of the models.
Convergence and mixing of each MCMC chain was determined by ensuring the effective sample size of each parameter was over 200.

We report posterior distributions for the model parameters in \cref{figure:netdivall}, and also for the compound parameters of net diversification ($\lambda - \mu$) and extinction fraction ($\mu / \lambda$) for each state.
Additionally, ancestral states at each node in the phylogeny were sampled jointly during the MCMC analyses every 100 generations.
% Itay says remove but some reviewers were interested in the distribution of the states. I say leave we don't need to discuss. I'll mention briefly.
Ancestral state estimations for all models show the maximum \emph{a posteriori} estimates of the marginal probability distributions for each of the 650 internal nodes for each of the models in \cref{figure:netdivall}. (\cref{suppfigure:DPnodipasr,suppfigure:DPnodipABasr,suppfigure:ICasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipasr,suppfigure:IDCDCPnodipABasr}).

### 2019-07-18 manuscript/results.tex
All co-authors input added, figures corrected

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates (\cref{suppfigure:asymmetric}).

>>>>

    \item Are conclusions robust to assumptions about hidden state transitions?
    Yes, we found that allowing different types of asymmetry in transitions within and between hidden states did not change our conclusions about net diversification differences.
    Hidden state models with asymmetric rates are, however, strongly preferred over models with equal rates between hidden states (\cref{supptable:asymmetry}), and they show stronger differences between some net diversification rates (\cref{suppfigure:asymmetric}).
    %Rosana added the following lines to alleviate the comment from Itay about hidden states
    The effect of the asymmetry of the hidden rate transitions  is better observed in the ancestral state estimations (\cref{suppfigure:DPnodipABasr,suppfigure:ICABasr,suppfigure:IDCDCPnodipABasr}), which show that moving out of state A (dark colors) happens quickly with rate $\alpha$,  whereas evolving out of hidden state B (light colors) is slow with rate $\beta$.
